A component-based DSL for multi-stencil programs

### 2015-07-21 WOLFHPC15/article/related.tex
wolfhpc15 21_07

A real case numerical simulation is most of the time composed of a set of numerical schemes (stencils computations), with one or more stencil shape (neighboorhood shape), and onto one or more data. Moreover, a numerical simulation also performs additionnal auxiliary computations which do not involve neighborhood, called local computations. Solutions like Pochoir or PATUS consider the parallelization of a single stencil code, considering that stencil codes represent the main computation time of numerical simulations. However, by not taking into account the parallelization of the overall numerical simulation, those compilers also reduce the codes to shared memory systems. Actually using a distributed memory system, the MPI (Message Passing Interface)~\cite{Graham2009MSE} library still have to be used by the user, as well as the distribution of the mesh onto the different distant processors.

>>>>

However, a real case numerical simulation is not composed of a single stencil code as explained in Section~\ref{sect:multistencil}. A multi-stencil simulation computes more than one stencil computation, involving one or more stencil shapes, and additionnal local coputations. Solutions like Pochoir or PATUS handle the parallelization or the optimization of a single stencil code, considering that stencil codes represent the main computation time of numerical simulations. However, not taking into account the parallelization of the overall numerical simulation implies that those compilers are reduced to shared memory systems. Actually using a distributed memory system, the MPI (Message Passing Interface)~\cite{Graham2009MSE} library still have to be used by the user, as well as the distribution of the mesh onto the different distant processors.
